---
title: "my first markdown file"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
library(dplyr)
library(readr)
library(ggplot2)
```

## Reading the Data
This dataset shows all of the students' 5 favorite restaurants. We followed a specific data dictionary to input the data into the dataset which allows us to be consistent. 

```{r}
fav_restaurants <- read_csv("https://raw.githubusercontent.com/URstats/stat209-s18-allisonzhang9/master/fav_restaurants.csv")
```

## Plotting the Data
This is a bar graph that shows how many restaurants were entered under each type of cuisine.
```{r}
ggplot(fav_restaurants, aes(cuisine)) +
  geom_bar()
```

This is a scatter plot of how often we visit per year in relation to the cost of an average meal per person.
```{r}
ggplot(fav_restaurants, aes(yearly_visits, cost_per_person)) +
  geom_point()
```

This is a bar graph that shows where the restaurants are that were entered and how many of each there are.
```{r}
ggplot(fav_restaurants, aes(location)) +
  geom_bar()
```

