---
title: "Lab 09: Annotating Data Visualizations"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.height = 5)
knitr::opts_chunk$set(fig.width = 8.5)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(dpi = 300)

library(readr)
library(ggplot2)
library(dplyr)
library(viridis)
library(lubridate)
theme_set(theme_minimal())
```

## Pick a dataset

Today you'll have a choice of three datasets to work with. You can choose
either to investigate Donald Trump's approval rating:

```{r}
trump <- read_csv("https://statsmaths.github.io/stat_data/trump_approval.csv")
```

Pick a dataset (feel free to delete the others from the Rmd file if you would
like), and work on the instructions in the next section.

## Instructions

Your goal in this lab is to construct an interesting visualization with the
data that you choose above. You should make use of several manual annotations
in an effort to tell a visual story about the dataset. Below, you should
eventually provide a few sentences describing what you found in the dataset
and then a single plot illustrating the interesting aspects of the data.
You should incorporate some external information into your plot.

Note that you will certainly want to create many initial exploratory plots
before settling on a final one for analysis. This time, make sure you that you
upload both the Rmd and the html files to GitHub (remember, the final report
should have just one single visualization).

Also note that you will have to use the format `x = as.Date("2017-01-06")` to
add annotations to an axis that uses time as a component.

## Analysis

I found that Trump's highest approval ratings happened in the first 3 months of his presidency, with a huge spike on the 25th day of January. It is expected that his approval rating is high his first few months, which matches the graph, but most presidents keep generally high approval ratings for at least their first year. I also noticed Trump hit an all time low in approval ratings on August 4th, which I labeled on the graph. Trump's approval rating is rising now, which is also a trend for most presidents as most approval ratings tend to revert back to 50 percent in the long run. 

```{r}
ggplot(trump, aes(date,approve))+
  geom_point(aes(color= factor(month(date))), size=2)+
  annotate("text", x = as.Date("2017-08-03"), y = 36.8, label = "Lowest Approval Rating") +
  annotate("rect", xmin= as.Date("2017-01-06"), xmax= as.Date("2017-04-09"),
           ymin = 44, ymax = 49, fill = "blue", alpha = 0.1)+
  annotate("text", x=as.Date("2017-03-25"), y=49, label="Highest Approval Rating Time Period")
```









